Testing atlantisom: true biomass output from Atlantis

### 2019-04-30 TrueBioTest.Rmd
add refs, update html

---
title: "Testing atlantisom: true biomass output from Atlantis"
author: "Sarah Gaichas and Christine Stawitz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

First, you will want to set up libraries and install atlantisom if you haven't already.

@@

If you want to load the local of the atlantisom R package, use devtools. The R package here [@`citation(here)'] is helpful for installing from your local atlantisom directory, as it avoids hardcoding the specific location. The code below is not running from our local atlantisom directory and is not evaluated:

@@

Our directory structure is set up to take advantage of `here()' to allow setup on a different computer.

@@

Now the R object `results` with the comprehensive results from the Atlantis model has been read in. It is also saved as an .RData file titled "output[scenario.name]run_truth.RData" in the directory with the model output, so that later analyses can use 'load()' instead of taking the time to rerun `atlantisom::run_truth()'.

@@

To create a survey, the user specifies the timing of the survey, which species are captured, the spatial coverage of the survey, the species-specific survey efficieny ("q"), and the selectivity at age for each species.

@@

```{r surveyNbased, fig.cap="Check weight at age generated from biomass_age$atoutput divided by nums$atoutput for first 32 groups.", fig.show="hold"}

@@

@@

#all species comparison, time intervals hardcoded for NEUS and NOBA
compareB_N <-ggplot() +
  geom_line(data=surveyB_fromN, aes(x=time/5,y=atoutput, color="survey census N->B"), 
            alpha = 3/10) +
  geom_point(data=atBtxt2tidy, aes(x=Time/365,y=biomass, color="txt output true B"),
             alpha = 3/10) + 
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

@@

>>>>

---
title: "Testing atlantisom: true biomass output from Atlantis"
author: "Sarah Gaichas and Christine Stawitz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
bibliography: "packages.bib"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'knitr', 'rmarkdown', 'tidyr', 'dplyr', 'ggplot2',
  'data.table', 'here', 'ggforce', 'ggthemes'
), 'packages.bib')
```

@@

First, you will want to set up libraries and install atlantisom if you haven't already. This document is written in in R Markdown [@R-rmarkdown], and we use several packages to produce the outputs [@R-tidyr; @R-dplyr; @R-ggplot2; @R-here; @R-ggforce; @R-ggthemes].

@@

If you want to load the local of the atlantisom R package, use devtools. The R package here is helpful for installing from your local atlantisom directory, as it avoids hardcoding the specific location. The code below is not running from our local atlantisom directory and is not evaluated:

@@

Our directory structure is set up to take advantage of `here()` to allow setup on a different computer.

@@

Now the R object `results` with the comprehensive results from the Atlantis model has been read in. It is also saved as an .RData file titled "output[scenario.name]run_truth.RData" in the directory with the model output, so that later analyses can use `base::load()` instead of taking the time to rerun `atlantisom::run_truth()`.

@@

To create a survey, the user specifies the timing of the survey, which species are captured, the spatial coverage of the survey, the species-specific survey efficiency ("q"), and the selectivity at age for each species.

@@

```{r surveyNbased, fig.cap="Check weight at age generated from biomass_age$atoutput divided by nums$atoutput for up to 48 groups.", fig.show="hold"}

@@

wtagecheck + 
  facet_wrap_paginate(~species, ncol=4, nrow=4, page=3, scales="free")

@@

#all species comparison, time intervals hardcoded for NEUS and NOBA
compareB_N <-ggplot() +
  geom_line(data=surveyB_fromN, aes(x=time/5,y=atoutput, color="survey census N->B"), 
            alpha = 10/10) +
  geom_point(data=atBtxt2tidy, aes(x=Time/365,y=biomass, color="txt output true B"),
             alpha = 1/10) + 
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

@@

We have more misses in the numbers with average weight estimation, so this needs more investigation and discussion. It may be best to have the survey index for testing derived directly from the true biomass output.

## References
